---
title: "INet"
subtitle: "Network Integration"
author: "Valeria Policastro et al."
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{INet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  knitr:::html_vignette:
    toc: yes
    toc_depth: 2
---


# INet

To answer the integration problem, we constructed the \texttt{INet Algorithm}, assuming the presence of a structure underneath the different networks with some similarities that we want to pull out. We generate a \texttt{Consensus Network} to give common information present underneath the different layers and a global view of the actors which play a fundamental role in the phenomenon of interest. In addition, the algorithm constructs a \texttt{Case Specific Network} for each network containing peculiar information of the single data type not present in all the others.


# INet package
```{r, library}
library(INet)
```

# Simulated data construction
```{r, load dataset}
 gI <- igraph::sample_pa(n=10,directed=FALSE)
 igraph::E(gI)$weight <- runif(igraph::ecount(gI),0.5,1)
 gII <- igraph::sample_pa(n=10,directed=FALSE)
 igraph::E(gII)$weight <- runif(igraph::ecount(gII),0.5,1)
 graphsList <- list(gI,gII)
```

# Pre Analysis
```{r}

densityNet(graphsList)
JWmatrix(graphsList)
JWmean(graphsList)
```



# Consensus network

A list of weighted adjacency matrices is needed. 
The nodes should be the same in all the matrices.

```{r}
 MatI <- igraph::as_adjacency_matrix(graph= gI,attr = "weight")
 MatII <- igraph::as_adjacency_matrix( graph= gII, attr = "weight")
 my_AdjMatrices <- list(MatI,MatII)
```


To construct the consensus network
```{r, consensus_function}
my_Consensus <- consensusNet(adjMatL=my_AdjMatrices, tolerance=0.1, theta=0.04, ThresholdConsensus=0.01, nitermax=50,ncores=2)
 my_Consensus
```



# Specific Network
```{r, specific-function}
specificNet(graphsL=graphsList,graphConsensus=my_Consensus$graphConsensus)
```
